Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models

### 2020-12-02 analysis/paper/paper.tex
made the font size 10 in all tables in main document and appendix

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models},
  pdfauthor={Kevin E. See1,, Michael W. Ackerman1, Richard A. Carmichael1, Sarah L. Hoffmann1, and Chris Beasley1},
  pdfkeywords={carrying capacity; quantile regression; random forests; Chinook; quantile random forest},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% double spacing
\usepackage{setspace}
\doublespacing
% to double space figure captions
\usepackage{caption}
\captionsetup{font = doublespacing}

@@

\title{Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models}
\author{Kevin E. See\textsuperscript{1,*}, Michael W. Ackerman\textsuperscript{1}, Richard A. Carmichael\textsuperscript{1}, Sarah L. Hoffmann\textsuperscript{1}, and Chris Beasley\textsuperscript{1}}
\date{December 01, 2020}

@@

Most studies that have investigated fish-habitat relationships focus on predicting a species' distribution (presence / absence) or the average abundance or density: neither of which can be easily manipulated to predict carrying capacity. Further, many of these studies focus on only one or two measures of habitat. Fausch et al. (1988) conducted a thorough review of attempts to predict the abundance of fish from measurable habitat covariates from 1950 to 1985 and found that the vast majority of multiple linear regression models failed to detect a significant fish-habitat signal. Since that review, there has been progress in identifying some fish-habitat relationships for several salmonid species. Nickelson et al. (1992) demonstrated that juvenile coho salmon (\emph{O. kisutch}) were found in higher densities within pool habitat on the Oregon coast. Similarly, pool and pond densities were good predictors of coho smolt densities in western Washington (Sharma and Hilborn 2001). Bryant and Woodsmith (2009) found that juvenile coho abundance was positively related to large wood at the reach scale; however their results demonstrated a negative relationship between abundance and the number of pools. Braun and Reynolds (2011) similarly found positive associations between spawner densities of sockeye salmon (\emph{O. nerka}) in the Fraser River and large wood, in addition to positive relationships to percent undercuts and percent pools. Densities of adult spawning coho were also higher in forested areas compared to urban or agricultural areas in the Snohomish River watershed (Pess et al. 2002). Mossop and Bradford (2006) examined juvenile Chinook salmon (\emph{O. tshawytscha}) in the Yukon River and found positive correlations between the log of fish density and several metrics related to residual pool dimensions and large woody debris abundance as well as a negative correlation between fish density and gradient. These studies were focused on predicting observed fish densities, not necessarily capacity, and for most of them the predictive extent is limited to a particular watershed. In addition, they all assumed some form of linear fish-habitat relationship which often results in weak predictive power.

@@

\caption{\label{tab:fish-hab-sites}The number of unique sites, by watershed, with paired fish-habitat data used to populate the spring/summer-run Chinook salmon parr capacity QRF model}
\centering
\begin{tabular}[t]{lrl}
\toprule
Watershed & n Sites & Percent\\
\midrule
Entiat & 61 & 18.7\%\\
John Day & 75 & 22.9\%\\
Lemhi & 33 & 10.1\%\\
Minam & 20 & 6.1\%\\
South Fork Salmon & 30 & 9.2\%\\
Upper Grande Ronde & 86 & 26.3\%\\
Wenatchee & 22 & 6.7\%\\
Total & 327 & 100.0\%\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:select-mets-table}Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer-run Chinook salmon parr capacity. Metrics are ranked in order of relative importance.}
\centering
\begin{tabular}[t]{rll>{\raggedright\arraybackslash}p{3in}}
\toprule
Rank & Metric & Metric Category & Description\\
\midrule
1 & Wetted Width & Size & Average width of the wetted polygon for a site.\\
2 & Discharge & Size & The sum of station discharge across all  stations.  Station discharge is calculated as depth x velocity x station increment for all stations except first and last.  Station discharge for first and last station is 0.5 x station width x depth x velocity.\\
3 & Avg. August Temp. & Temperature & Average predicted daily August temperature from NorWest, averaged across the years 2002-2011.\\
4 & Width:Depth Ratio & Complexity & Average width to depth ratio of the wetted channel measured from cross-sections. Depths represent an average of depths along each cross-section.\\
5 & Fines & Substrate & Average percentage of pool tail substrates comprised of sediment <6 mm.\\
6 & Fish Cover & Cover & Percent of wetted area with the following types of cover: aquatic vegetation, artificial, woody debris, and terrestrial vegetation.\\
7 & Channel Unit Frequency & ChannelUnit & Number of channel units per 100 meters.\\
8 & Depth Complexity & Complexity & Standard Deviation of water depths within the wetted channel.\\
9 & Large Wood Freq. in Pools & Wood & Total volume of  large wood pieces  within the wetted channel and Slow Water/Pool channel units, scaled by site length.\\
10 & Riparian Canopy & Riparian & Percent of riparian canopy with some vegetation.\\
11 & Substrate: D16 & Substrate & Diameter of the 16th percentile particle derived from pebble counts.\\
12 & Braidedness & Complexity & Ratio of the total length of the wetted mainstem channel plus side channels and the length of the mainstem channel.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:gaa-covars}Globally available attribute (GAA) habitat covariates used to extrapolate quantile random forest (QRF) model predictions of spring/summer-run Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.}
\centering
\begin{tabular}[t]{lllrr}
\toprule
Covariate & Units & Spatial Scale & Estimate & Std. Error\\
\midrule
Temeprature Range & C & Reach-2km & -0.044 & 0.081\\
Elevation & m & Site-300m & -0.243 & 0.155\\
CHaMP Watershed & - & Region & - & -\\
Natural Class PCA 1 & - & Watershed-HUC12 & -0.092 & 0.070\\
Disturbance Class PCA 1 & - & Watershed-HUC12 & -0.064 & 0.064\\
Drainage Area (sqrt) & km$^2$ (square root) & Reach-2km & -0.141 & 0.077\\
Stream Power & - & Reach-2km & 0.049 & 0.033\\
Slope & m/m & Reach-2km & -0.513 & 0.100\\
Channel Type & - & Site-300m & - & -\\
Bankfull Width - modeled & m & Site-300m & 0.216 & 0.099\\
NorWeST Aug. Temperature & C & Reach-2km & -0.149 & 0.119\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:extrap-r2-table}Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.}
\centering
\begin{tabular}[t]{llrr}
\toprule
Model & Response & $r^2$ & Adjusted $r^2$\\
\midrule
CHaMP & fish/m & 0.481 & 0.454\\
non-CHaMP & fish/m & 0.360 & 0.339\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sr-table}Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile random forest (QRF) model. Numbers in parentheses are coefficients of variation.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{1in}rll>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}}
\toprule
Population & n Yrs & Adult Data & Parr Data & Beverton Holt & Ricker & Hockey Stick & QRF\\
\midrule
Catherine Creek & 20 & Spawners & RST & 135,387 (0.269) & 103,021 (0.141) & 99,921 (0.21) & 190,857 (0.162)\\
Chiwawa River & 20 & Spawners & Parr Surveys & 248,586 (0.24) & 166,139 (0.148) & 174,216 (0.184) & 216,451 (0.363)\\
Hayden Creek & 7 & Spawners & RST & 58,394 (0.244) & 65,958 (0.195) & 48,351 (0.174) & 121,676 (0.202)\\
Lostine River & 17 & Redds & RST & 196,259 (0.24) & 146,982 (0.159) & 144,415 (0.201) & 152,493 (0.316)\\
Minam River & 14 & Spawners & RST & 1,309,223 (2.18) & 484,810 (1.444) & 662,802 (1.726) & 365,338 (0.261)\\
South Fork Salmon River & 17 & Redds & RST & 87,260 (0.407) & 62,456 (0.265) & 64,654 (0.317) & 221,362 (0.142)\\
Tucannon River & 27 & Redds & RST & 4,791,131 (13.016) & 1,234,653 (8.566) & 1,922,692 (10.082) & 529,223 (0.196)\\
Upper Grande Ronde River & 8 & Spawners & RST & 171,607 (0.388) & 168,137 (0.298) & 127,052 (0.317) & 200,228 (0.23)\\
Upper Lemhi & 7 & Spawners & RST & 333,229 (0.322) & 229,635 (0.212) & 242,637 (0.252) & 269,626 (0.217)\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models},
  pdfauthor={Kevin E. See1,, Michael W. Ackerman1, Richard A. Carmichael1, Sarah L. Hoffmann1, and Chris Beasley1},
  pdfkeywords={carrying capacity; Chinook salmon; quantile random forest; quantile regression; random forests},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% double spacing
\usepackage{setspace}
\doublespacing
% to double space figure captions
\usepackage{caption}
\captionsetup{font = doublespacing}

@@

\title{Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models}
\author{Kevin E. See\textsuperscript{1,*}, Michael W. Ackerman\textsuperscript{1}, Richard A. Carmichael\textsuperscript{1}, Sarah L. Hoffmann\textsuperscript{1}, and Chris Beasley\textsuperscript{1}}
\date{December 02, 2020}

@@

Most studies that have investigated fish-habitat relationships focus on predicting a species' distribution (presence/absence) or the average abundance or density: neither of which can be easily manipulated to predict carrying capacity. Further, many of these studies focus on only one or two measures of habitat. Fausch et al. (1988) conducted a thorough review of attempts to predict the abundance of fish from measurable habitat covariates from 1950 to 1985 and found that the vast majority of multiple linear regression models failed to detect a significant fish-habitat signal. Since that review, there has been progress in identifying some fish-habitat relationships for several salmonid species. Nickelson et al. (1992) demonstrated that juvenile coho salmon (\emph{O. kisutch}) were found in higher densities within pool habitat on the Oregon coast. Similarly, pool and pond densities were good predictors of coho smolt densities in western Washington (Sharma and Hilborn 2001). Bryant and Woodsmith (2009) found that juvenile coho abundance was positively related to large wood at the reach scale; however their results demonstrated a negative relationship between abundance and the number of pools. Braun and Reynolds (2011) similarly found positive associations between spawner densities of sockeye salmon (\emph{O. nerka}) in the Fraser River and large wood, in addition to positive relationships to percent undercuts and percent pools. Densities of adult spawning coho were also higher in forested areas compared to urban or agricultural areas in the Snohomish River watershed (Pess et al. 2002). Mossop and Bradford (2006) examined juvenile Chinook salmon (\emph{O. tshawytscha}) in the Yukon River and found positive correlations between the log of fish density and several metrics related to residual pool dimensions and large woody debris abundance as well as a negative correlation between fish density and gradient. These studies were focused on predicting observed fish densities, not necessarily capacity, and for most of them the predictive extent is limited to a particular watershed. In addition, they all assumed some form of linear fish-habitat relationship which often results in weak predictive power.

@@

\caption{\label{tab:fish-hab-sites}The number of unique sites, by watershed, with paired fish-habitat data used to populate the spring/summer-run Chinook salmon parr capacity QRF model}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrl}
\toprule
Watershed & n Sites & Percent\\
\midrule
Entiat & 61 & 18.7\%\\
John Day & 75 & 22.9\%\\
Lemhi & 33 & 10.1\%\\
Minam & 20 & 6.1\%\\
South Fork Salmon & 30 & 9.2\%\\
Upper Grande Ronde & 86 & 26.3\%\\
Wenatchee & 22 & 6.7\%\\
Total & 327 & 100.0\%\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:select-mets-table}Habitat metrics and descriptions of metrics included in the QRF model to predict spring/summer-run Chinook salmon parr capacity. Metrics are ranked in order of relative importance.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{rll>{\raggedright\arraybackslash}p{3in}}
\toprule
Rank & Metric & Metric Category & Description\\
\midrule
1 & Wetted Width & Size & Average width of the wetted polygon for a site.\\
2 & Discharge & Size & The sum of station discharge across all  stations.  Station discharge is calculated as depth x velocity x station increment for all stations except first and last.  Station discharge for first and last station is 0.5 x station width x depth x velocity.\\
3 & Avg. August Temp. & Temperature & Average predicted daily August temperature from NorWest, averaged across the years 2002-2011.\\
4 & Width:Depth Ratio & Complexity & Average width to depth ratio of the wetted channel measured from cross-sections. Depths represent an average of depths along each cross-section.\\
5 & Fines & Substrate & Average percentage of pool tail substrates comprised of sediment <6 mm.\\
6 & Fish Cover & Cover & Percent of wetted area with the following types of cover: aquatic vegetation, artificial, woody debris, and terrestrial vegetation.\\
7 & Channel Unit Frequency & ChannelUnit & Number of channel units per 100 meters.\\
8 & Depth Complexity & Complexity & Standard Deviation of water depths within the wetted channel.\\
9 & Large Wood Freq. in Pools & Wood & Total volume of  large wood pieces  within the wetted channel and Slow Water/Pool channel units, scaled by site length.\\
10 & Riparian Canopy & Riparian & Percent of riparian canopy with some vegetation.\\
11 & Substrate: D16 & Substrate & Diameter of the 16th percentile particle derived from pebble counts.\\
12 & Braidedness & Complexity & Ratio of the total length of the wetted mainstem channel plus side channels and the length of the mainstem channel.\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:gaa-covars}Globally available attribute (GAA) habitat covariates used to extrapolate quantile random forest (QRF) model predictions of spring/summer-run Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllrr}
\toprule
Covariate & Units & Spatial Scale & Estimate & Std. Error\\
\midrule
Temeprature Range & C & Reach-2km & -0.044 & 0.081\\
Elevation & m & Site-300m & -0.243 & 0.155\\
CHaMP Watershed & - & Region & - & -\\
Natural Class PCA 1 & - & Watershed-HUC12 & -0.092 & 0.070\\
Disturbance Class PCA 1 & - & Watershed-HUC12 & -0.064 & 0.064\\
Drainage Area (sqrt) & km$^2$ (square root) & Reach-2km & -0.141 & 0.077\\
Stream Power & - & Reach-2km & 0.049 & 0.033\\
Slope & m/m & Reach-2km & -0.513 & 0.100\\
Channel Type & - & Site-300m & - & -\\
Bankfull Width - modeled & m & Site-300m & 0.216 & 0.099\\
NorWeST Aug. Temperature & C & Reach-2km & -0.149 & 0.119\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:extrap-r2-table}Summary of extrapolation model fits, split by whether the extrapolation model used CHaMP watershed as a covariate or not.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{llrr}
\toprule
Model & Response & $r^2$ & Adjusted $r^2$\\
\midrule
CHaMP & fish/m & 0.481 & 0.454\\
non-CHaMP & fish/m & 0.360 & 0.339\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:sr-table}Estimates of parr capacity from both spawner-recruit data (Beverton-Holt, Ricker, hockey stick) and from extrapolated estimates of parr capacity from the quantile random forest (QRF) model. Numbers in parentheses are coefficients of variation.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{1in}rll>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}>{\raggedright\arraybackslash}p{0.5in}}
\toprule
Population & n Yrs & Adult Data & Parr Data & Beverton Holt & Ricker & Hockey Stick & QRF\\
\midrule
Catherine Creek & 20 & Spawners & RST & 135,387 (0.269) & 103,021 (0.141) & 99,921 (0.21) & 190,857 (0.162)\\
Chiwawa River & 20 & Spawners & Parr Surveys & 248,586 (0.24) & 166,139 (0.148) & 174,216 (0.184) & 216,451 (0.363)\\
Hayden Creek & 7 & Spawners & RST & 58,394 (0.244) & 65,958 (0.195) & 48,351 (0.174) & 121,676 (0.202)\\
Lostine River & 17 & Redds & RST & 196,259 (0.24) & 146,982 (0.159) & 144,415 (0.201) & 152,493 (0.316)\\
Minam River & 14 & Spawners & RST & 1,309,223 (2.18) & 484,810 (1.444) & 662,802 (1.726) & 365,338 (0.261)\\
South Fork Salmon River & 17 & Redds & RST & 87,260 (0.407) & 62,456 (0.265) & 64,654 (0.317) & 221,362 (0.142)\\
Tucannon River & 27 & Redds & RST & 4,791,131 (13.016) & 1,234,653 (8.566) & 1,922,692 (10.082) & 529,223 (0.196)\\
Upper Grande Ronde River & 8 & Spawners & RST & 171,607 (0.388) & 168,137 (0.298) & 127,052 (0.317) & 200,228 (0.23)\\
Upper Lemhi & 7 & Spawners & RST & 333,229 (0.322) & 229,635 (0.212) & 242,637 (0.252) & 269,626 (0.217)\\
\bottomrule
\end{tabular}
\end{table}
